 

### 2023-03-02 thesis.Rmd
Adding rayshader to Madagascar maps
Revisions to make dplyr::select command run without errors, revisions to Paper 3

    # pandoc_args: ['--lua-filter=section-bibliographies.lua.txt']
    # pandoc_args: ['--lua-filter=multibib.lua']

@@

{\ Daniel Arias}

@@

Imperdiet sed euismod nisi porta lorem mollis aliquam. Eget lorem dolor sed viverra ipsum nunc aliquet bibendum enim. Eget lorem dolor sed viverra. Vitae proin sagittis nisl rhoncus mattis. Mi sit amet mauris commodo quis imperdiet massa tincidunt. Quis auctor elit sed vulputate mi. Augue eget arcu dictum varius duis at consectetur lorem. Commodo elit at imperdiet dui accumsan sit amet. Consequat semper viverra nam libero justo laoreet sit. Quis hendrerit dolor magna eget est lorem ipsum. Eget arcu dictum varius duis at consectetur lorem. Fermentum posuere urna nec tincidunt praesent semper feugiat. Integer quis auctor elit sed vulputate mi sit amet. Ultricies integer quis auctor elit. Metus vulputate eu scelerisque felis imperdiet proin fermentum. Ut porttitor leo a diam sollicitudin tempor id eu nisl. Cras adipiscing enim eu turpis egestas. Cursus euismod quis viverra nibh cras pulvinar mattis nunc sed.[@vaidyanathanEvaluationInternetSearches2022]

>>>>

    # pandoc_args: ['--lua-filter=section-bibliographies.lua.txt']
    # pandoc_args: ['--lua-filter=multibib.lua']
  # pdf_document:
    # pandoc_args: !expr acronymsdown::add_filter()
    # number_sections: TRUE

@@

{\ Daniel Alejandro Arias}

@@

We take as our first credible signal of the imminent availability of multiple safe and effective COVID-19 vaccines to be November 16, 2020. On November 9^th^, Pzifer announced than early vaccine trial data showed 90% efficacy;[@thomasPfizerEarlyData2020] on the 16^th^, Moderna similarly announced preliminary results showing 94.5% efficacy for their vaccine.[@gradyEarlyDataShow2020] While U.S. Food and Drug Administration (FDA) Emergency Use Authorization (EUA) was not granted until December, the concurrent announcements of vaccine efficacy were widely reported and interpreted by many public health practitioners, policymakers, and the general public as a substantial signal of a new phase of the pandemic, with Moderna’s chief executive officer calling the news “a game changer” in the fight against COVID-19.
